The \dealii Library, Version 9.2

### 2020-05-24 9.2/paper.tex
Add a todo.

Large-scale simulations with 304,128 cores have revealed bottlenecks in setup
routines due to the usage of expensive collective operations
like \texttt{MPI\_Allgather()} and \texttt{MPI\_\allowbreak Alltoall()}, storing
problem sizes and offsets from all processors in the MPI universe.
In release 9.2, we have replaced these functions in favor of
consensus algorithms~\cite{hoefler2010scalable}, which can be
found in the namespace \texttt{Utilities::\allowbreak MPI::\allowbreak ConsensusAlgorithms} (short: \texttt{CA}).
Now, only the locally relevant information about the index ranges is
(re)computed when needed, which, for more than 100 MPI processes, uses
point-to-point communications and a single \texttt{MPI\_IBarrier()}.

@@

Users can apply the new algorithms for their own dynamic-sparse problems by
providing a list of target
processes and pack/unpack routines either by implementing the interface
\texttt{CA::\allowbreak Process} or by providing \texttt{std::function}
objects to \texttt{CA::AnonymousProcess}.
\todo[inline]{Aren't the target processes the result of the operation, and the
  input global numbers of indices that we request?}

By replacing the collective communications during setup and removing the arrays
that contain information for each process (enabled by the application of consensus
algorithms and other modifications---a full list of modifications leading to this
improvement can be found online), we were able to significantly improve the setup
time for large-scale simulations and to solve a Poisson problem with multigrid
with 12T unknowns.
\todo[inline]{Where did we solve for 12T unknowns? The largest I [Martin] have done is 2.1T unknowns.}
Figure~\ref{} compares the timings of a simulation (incl. setup) with the
previous release 9.1 and with the current release 9.2.
{\color{red}TODO[Peter/Martin] description of the results}

The new code has been also applied to solve problems with adaptively refined
meshes with more than 4B unknowns. {\color{red}TODO[Timo]}

@@

\dealii can interface with many other libraries:
\begin{multicols}{3}
\begin{itemize}
\item ADOL-C \cite{Griewank1996a,adol-c}
\item ARPACK \cite{arpack}
\item Assimp \cite{assimp}
\item BLAS and LAPACK \cite{lapack}
\item cuSOLVER \cite{cusolver}
\item cuSPARSE \cite{cusparse}
\item Gmsh \cite{geuzaine2009gmsh}
\item GSL \cite{gsl2016}
\item Ginkgo \cite{ginkgo-web-page}
\item HDF5 \cite{hdf5}
\item METIS \cite{karypis1998fast}
\item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
\item muparser \cite{muparser-web-page}
\item nanoflann \cite{nanoflann}
\item NetCDF \cite{rew1990netcdf}
\item OpenCASCADE \cite{opencascade-web-page}
\item p4est \cite{p4est}
\item PETSc \cite{petsc-user-ref,petsc-web-page}
\item ROL \cite{ridzal2014rapid}
\item ScaLAPACK \cite{slug}
\item SLEPc \cite{Hernandez:2005:SSF}
\item SUNDIALS \cite{sundials}
\item SymEngine \cite{symengine-web-page}
\item TBB \cite{Rei07}
\item Trilinos \cite{trilinos,trilinos-web-page}
\item UMFPACK \cite{umfpack}
\end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.

>>>>

Large-scale simulations with 304,128 cores have revealed bottlenecks in release 
9.1 during initialization of a number of distributed data structures due to the usage of expensive collective operations 
like \texttt{MPI\_Allgather()} and \texttt{MPI\_\allowbreak
  Alltoall()}. Typical examples are the
pre-computation of those indices of the vector entries (or
other linear index ranges) owned by
each process, which were previously stored in  an array on every process. 
This information is needed to set up 
the  \texttt{Utilities::MPI::Par\-ti\-ti\-oner} class.
In release 9.2, we have replaced these functions in favor of
consensus algorithms~\cite{hoefler2010scalable}, which can be
found in the namespace \texttt{Utilities::\allowbreak MPI::\allowbreak ConsensusAlgorithms} (short: \texttt{CA}).
Now, only the locally relevant information about the index ranges is
(re)computed when needed, which, for more than 100 MPI processes, uses
point-to-point communications and a single \texttt{MPI\_IBarrier()}.

@@

Users can apply the new algorithms for their own dynamic-sparse problems by
providing a list of target
processes and pack/unpack routines either by implementing the interface
\texttt{CA::\allowbreak Process} or by providing \texttt{std::function}
objects to \texttt{CA::AnonymousProcess}.

\todo[inline]{Aren't the target processes the result of the operation, and the
  input global numbers of indices that we request?}

By replacing the collective communications during set up and removing the arrays
that contain information for each process (enabled by the application of consensus
algorithms and other modifications---a full list of modifications leading to this
improvement can be found online), we were able to significantly
improve the set up
time for large-scale simulations and to solve a Poisson problem with multigrid
with \num{12e12} unknowns.
\todo[inline]{Where did we solve for 12T unknowns? The largest I [Martin] have done is 2.1T unknowns.}
Figure~\ref{} compares the timings of a simulation (including set up) with the
previous release 9.1 and with the current release 9.2.
{\color{red}TODO[Peter/Martin] description of the results}

The new code has been also applied to solve problems with adaptively refined
meshes with more than \num{4e9} unknowns. {\color{red}TODO[Timo]}

@@

\todo[inline]{Need to add the particles paper by Gassmoeller et al.}

\dealii can interface with many other libraries:
\todo[inline]{We picked up gingko. Anything else?}
\begin{multicols}{3}
\begin{itemize}
\item ADOL-C \cite{Griewank1996a,adol-c}
\item ARPACK \cite{arpack}
\item Assimp \cite{assimp}
\item BLAS and LAPACK \cite{lapack}
\item cuSOLVER \cite{cusolver}
\item cuSPARSE \cite{cusparse}
\item Gmsh \cite{geuzaine2009gmsh}
\item GSL \cite{gsl2016}
\item Ginkgo \cite{ginkgo-web-page}
\item HDF5 \cite{hdf5}
\item METIS \cite{karypis1998fast}
\item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
\item muparser \cite{muparser-web-page}
\item nanoflann \cite{nanoflann}
\item NetCDF \cite{rew1990netcdf}
\item OpenCASCADE \cite{opencascade-web-page}
\item p4est \cite{p4est}
\item PETSc \cite{petsc-user-ref,petsc-web-page}
\item ROL \cite{ridzal2014rapid}
\item ScaLAPACK \cite{slug}
\item SLEPc \cite{Hernandez:2005:SSF}
\item SUNDIALS \cite{sundials}
\item SymEngine \cite{symengine-web-page}
\item TBB \cite{Rei07}
\item Trilinos \cite{trilinos,trilinos-web-page}
\item UMFPACK \cite{umfpack}
\end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.
